### 2023-12-11 README.Rmd
update readme

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `renv::restore` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.qmd` and render to produce the `paper.docx`, or run `quarto::quarto_render("analysis/paper/paper.qmd")` in the R console

>>>>

You can download the compendium as a zip from from this URL:
[master.zip](/archive/refs/heads/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `renv::restore` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- to re-run the code that performs the data analysis and creates the visualisations, look in the `scripts` folder and run the R and Rev script files in order. The file names contain numbers that indicate the correct order. You will need to install [RevBayes](https://revbayes.github.io/) to run some of these files. 
- finally, open `analysis/paper/paper.qmd` and render to produce the `paper.docx`, or run `quarto::quarto_render("analysis/paper/paper.qmd")` in the R console. Note that this file does not run any analysis code, it only combines the previously generated figures with the text of the manuscript.
